\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{comment}
\input{glyphtounicode}

% Font options
\usepackage[T1]{fontenc}
% \usepackage[default]{lato} % If you want a sans-serif font, uncomment this

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge \scshape Suhas Kamath} \\ \vspace{1pt}
    \small +91-8310235211 $|$ \href{mailto:suhaskamath672@gmail.com}{\underline{suhaskamath672@gmail.com}}  $|$
    \href{mailto:suhaskamath@iisc.ac.in}{\underline{suhaskamath@iisc.ac.in}} \\ \vspace{1pt}
    \href{https://suhaskamath2712.github.io/}{\underline{suhaskamath2712.github.io}} $|$
    \href{https://github.com/suhaskamath2712}{\underline{GitHub}} $|$
    \href{https://www.linkedin.com/in/suhas-kamath-4472b1215/}{\underline{LinkedIn}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{M. Tech (Computational \& Data Science) student studying at Indian Institute of Science, Bengaluru. My work focuses on Databases and Query Optimization.}
  \vspace{5pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Science}{Bengaluru, Karnataka}
      {Master of Technology - Computational \& Data Science}{July 2025 -- June 2027}
  \resumeSubHeadingListEnd
  
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Mysore}{Mysore, Karnataka}
      {Master of Computer Applications}{February 2023 -- May 2025}
  \resumeSubHeadingListEnd
  
  \resumeSubHeadingListStart
    \resumeSubheading
      {Curtin University}{Perth, Western Australia}
      {Bachelor of Technology - Computer Systems \& Networking}{February 2020 -- January 2023}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Technical Content Writer}{April 2023 -- August 2023}
      {}{Freelance}
      \resumeItemListStart
        \resumeItem{Wrote web articles on various Java libraries, including Spring Boot and Hibernate.}
      \resumeItemListEnd

    \resumeSubheading
      {DevOps Intern}{November 2021 -- February 2022}
      {Invantest Sdn. Bhd.}{Penang, Malaysia}
      \resumeItemListStart
        \resumeItem{Automated installation of application using automation software such as Ansible.}
        \resumeItem{Worked with shell scripting and task scheduling in Linux CLI-based systems.}
        \resumeItem{Hosted a self-maintained instance of GitLab.}
        \resumeItem{Hosted an instance of Ansible Tower (Ansible AWX).}
        \resumeItem{Worked with Docker and Kubernetes.}
      \resumeItemListEnd

    \resumeSubheading
      {Kinsajasa Sdn. Bhd.}{December 2020 -- February 2021}
      {}{Malaysia}
      \resumeItemListStart
        \resumeItem{Learnt Visual Basic for Excel (VBA).}
        \resumeItem{Programmed a Microsoft Excel Workbook using macros to make it into an
interactive database for recording status of company's equipment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Query Plan Equivalence using LLM} $|$ \emph{\href{https://github.com/suhaskamath2712/E0261_P11}{\underline{View Code}}}}{}
          \resumeItemListStart
            \resumeItem{Developed a Java-based program to semantically equate two query plans using Large Language Models (LLMs).}
            \resumeItem{Completed as part of the E0261 course project.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{QPostgres} $|$ \emph{\href{https://github.com/suhaskamath2712/qpostgres}{\underline{View Code}}}}{}
          \resumeItemListStart
            \resumeItem{Modified PostgreSQL to support the Q-Error histogram, as developed by Moerkotte et. al.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{PG\_Pyramid} $|$ \emph{\href{https://github.com/suhaskamath2712/pg_pyramid}{\underline{View Code}}}}{}
          \resumeItemListStart
            \resumeItem{Created a pyramid indexing extension for PostgreSQL based on the paper by Berchtold et. al.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{LLM Training Pipeline}}{}
          \resumeItemListStart
            \resumeItem{Developed a Python-based program using Apache Spark for preprocessing and DeepSpeed for distributed training of Large Language Models.}
            \resumeItem{Completed as part of the DS256 course project.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Parallelised K-Means Clustering} $|$ \emph{\href{https://github.com/suhaskamath2712/ISS_Assignment/tree/main/OpenMP}{\underline{View Code}}}}{}
          \resumeItemListStart
            \resumeItem{Implemented parallelised K-Means clustering using OpenMP.}
            \resumeItem{Completed as part of the DS221 course project.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Parallel Matrix-Vector Multiplication} $|$ \emph{\href{https://github.com/suhaskamath2712/ISS_Assignment/tree/main/MPI}{\underline{View Code}}}}{}
          \resumeItemListStart
            \resumeItem{Implemented parallel matrix-vector multiplication using MPI.}
            \resumeItem{Completed as part of the DS221 course project.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXTRACURRICULARS-----------
\section{Extracurricular Activities}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Lead Volunteer, ACM SIGMOD/PODS 2026} $|$ \emph{\href{https://2026.sigmod.org/}{\underline{Website}}}}{}
          \resumeItemListStart
            \resumeItem{Served as the lead volunteer for the ACM SIGMOD/PODS 2026 conference.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{IISc Calendar 2026 Designer} $|$ \emph{\href{https://www.linkedin.com/posts/institution-innovation-council-iic-iisc\_iic-calendar-designs-ugcPost-7414228156267700224-qsvM?utm\_source=share\&utm\_medium=member\_desktop\&rcm=ACoAADZTrDcB0Xc3ZBalmQDPo8MAmC64FkrdKAU}{\underline{LinkedIn}}}}{}
          \resumeItemListStart
            \resumeItem{Designed the official Institution's Innovation Council (IIC) calendar for the Indian Institute of Science for the year 2026.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\begin{comment}
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Voeux} $|$ \emph{\href{https://google.com}{\underline{Live}}}}{}
          \resumeItemListStart
            \resumeItem{Created and launched a cross-device wallpaper download platform with \textbf{Next.js}, providing smooth navigation.}
            \resumeItem{Deployed secure authentication mechanisms with \textbf{JWT} and \textbf{NextAuth.js}, cutting login issues by 25\%.}
            \resumeItem{Curated a collection of high-quality wallpapers with new additions every 2 weeks to increase user engagement.}
            \resumeItem{Automated a web scraping pipeline with \textbf{Python}, \textbf{Selenium} and \textbf{MongoDB}, reducing manual work by 90\%.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{aSnippets} $|$ \emph{\href{https://google.com}{\underline{Live on Firefox store}}}}{}
          \resumeItemListStart
            \resumeItem{Introduced a \textbf{Chrome extension} enabling users to add, organize, and store text snippets, enhancing workflow.}
            \resumeItem{Leveraged \textbf{Manifest V3} for service workers and synchronized storage, resulting in a 30\% performance boost.}
            \resumeItem{Crafted user interfaces with \textbf{React} and \textbf{Tailwind CSS}, leveraging \textbf{TypeScript} for improved code reliability.}
            \resumeItem{Revamped application state management through \textbf{Redux Toolkit}, enhancing application performance by 20\%.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Game Matrix} $|$ \emph{\href{https://google.com}{\underline{Live}}} $|$ \emph{\href{https://github.com}{\underline{Github}}}}{}
          \resumeItemListStart
            \resumeItem{Launched an online platform that recommends similar games to users from a collection of over \textbf{20,000} titles.}
            \resumeItem{Achieved 80\% faster response time by markedly improving ML models and refining output generation processes.}
            \resumeItem{Constructed frontend interfaces using \textbf{Vue} and \textbf{Tailwind CSS} to create interactive and user-friendly designs.}
            \resumeItem{Elevated API performance by 20\% through refactoring backend built with \textbf{Python}, \textbf{Flask}, and \textbf{PostgreSQL}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

    %-----------ACHIEVEMENTS-----------
    \section{Achievements}
     \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{LeetCode}: Solved 550+ coding problems, covering diverse data structures and algorithmic concepts. \hfill \href{https://leetcode.com}{\underline{Profile}} \\
         \textbf{CodeForces}: Achieved highest online contest rating of 978 and solved over 100 programming problems. \hfill \href{https://codeforces.com}{\underline{Profile}}
        }}
     \end{itemize}
    
    %-----------CERTIFICATIONS-----------
    \section{Certifications}
     \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{Coursera}: Finished the complete Machine Learning Specialization on Coursera \hfill \href{https://coursera.org}{\underline{Certificate}}
        }}
     \end{itemize}
\end{comment}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Java, Python, HTML/CSS, SQL} \\
     \textbf{Libraries \& Frameworks}{: Numpy, Pandas, Matplotlib, Apache Spark, DeepSpeed, OpenMP, MPI} \\
     \textbf{Developer Tools}{: Microsoft Visual Studio, Jupyter Notebooks, Pycharm, Postman, Git/Github} \\
     \textbf{IT Constructs}{: Operating Systems, Data Structures and Algorithms, Database Management Systems (PostgreSQL)}\\
     \textbf{All Mainframe Technologies}{: COBOL, CICS, DB2, JCL, Easytrieves, Enndevor}
    }}
 \end{itemize}

\end{document}